Preprocessing

### 2023-08-17 docs/presentation/preprocess.Rmd
viz: likert for Q8, Q10

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpl.rds")
source("data/constants.R")
```

@@

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6_definition
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

clouds_q19 <- append(clouds_q19_q3, clouds_q19_q4)
clouds_q19$Everyone <- clouds$Q19_reason_for_rep
saveRDS(clouds_q19, file = "data/clouds_q19.rds")
```

@@

TODO: Rename Q6 labels
```{r eval=FALSE, include=FALSE}
analysis %<>%
  mutate(label = case_match(
    label,
    "Omit" ~ NA,
    "Standard" ~ "Assess Prior Work",
    "Experiment" ~ "Repeatable Experiments",
    "Data Collection" ~ "Data Collection",
    "Transparency/Extension" ~ "Transparency/Extension"
  ))
```

## Q7 Likert
```{r}
q7_to_likert <- function(data = analysis) {
  data %>%
    # make data for likert
    pivot_longer(cols = starts_with("Q7_value_")) %>%
    group_by(name, value) %>%
    summarise(n = n()) %>%
    mutate(value = factor(value, levels = agree_levels)) %>%
    replace_na(list(value = "Don't know")) %>%
    group_by(name) %>%
    mutate(perc = n / sum(n)) %>%
    mutate(
      yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
      idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
      nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
      start = case_match(
        value,
        "Strongly agree" ~ yeah + idk,
        "Agree" ~ idk,
        "Don't know" ~ -idk,
        "Disagree" ~ -idk - perc,
        "Strongly disagree" ~ -idk - nah - perc,
      )
    ) %>%
    ungroup() %>%
    dplyr::select(-c(yeah, nah, idk))
}
```

```{r Q8}
q7_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    q7_to_likert()
) %>%
  set_names(subfields)

@@

q7 <- append(q7_q3, q7_q4)
q7$Everyone <- q7_to_likert()
saveRDS(q7, file = "data/q7.rds")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")
```

>>>>

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpl.rds")
source("data/constants.R")

gen <- list()
```

@@

gen$q6 <- append(clouds_q6_q3, clouds_q6_q4)
gen$q6$Everyone <- clouds$Q6_definition
```

@@

gen$q19 <- append(clouds_q19_q3, clouds_q19_q4)
gen$q19$Everyone <- clouds$Q19_reason_for_rep
```

@@

## Q7 Likert
```{r}
q7_to_likert <- function(data = analysis) {
  data %>%
    # make data for likert
    pivot_longer(cols = starts_with("Q7_value_")) %>%
    group_by(name, value) %>%
    summarise(n = n()) %>%
    mutate(value = factor(value, levels = agree_levels)) %>%
    group_by(name) %>%
    mutate(perc = n / sum(n)) %>%
    mutate(
      yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
      idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
      nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
      start = case_match(
        value,
        "Strongly agree" ~ yeah + idk,
        "Agree" ~ idk,
        "Don't know" ~ -idk,
        "Disagree" ~ -idk - perc,
        "Strongly disagree" ~ -idk - nah - perc,
      )
    ) %>%
    ungroup() %>%
    drop_na(value) %>%
    dplyr::select(-c(yeah, nah, idk))
}
```

```{r Q7}
q7_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    q7_to_likert()
) %>%
  set_names(subfields)

@@

gen$q7 <- append(q7_q3, q7_q4)
gen$q7$Everyone <- q7_to_likert()
```

## Q8, Q10 to likert

```{r}
to_likert <- function(data = analysis, col_prefix) {
  data %>%
    # make data for likert
    pivot_longer(cols = starts_with(col_prefix)) %>%
    group_by(name, value) %>%
    summarise(n = n()) %>%
    mutate(value = factor(value, levels = likely_levels)) %>%
    group_by(name) %>%
    mutate(perc = n / sum(n)) %>%
    mutate(
      yeah = ifelse(any(
        value == "Somewhat likely to increase"),
        perc[value == "Somewhat likely to increase"], 0),
      idk = ifelse(
        any(value == "Not likely to affect"),
                   perc[value == "Not likely to affect"] / 2, 0),
      nah = ifelse(any(
        value == "Somewhat likely to decrease"), 
        perc[value == "Somewhat likely to decrease"], 0),
      start = case_match(
        value,
        "Very likely to increase" ~ yeah + idk,
        "Somewhat likely to increase" ~ idk,
        "Not likely to affect" ~ -idk,
        "Somewhat likely to decrease" ~ -idk - perc,
        "Very likely to decrease" ~ -idk - nah - perc,
      )
    ) %>%
    ungroup() %>%
    drop_na(value) %>%
    dplyr::select(-c(yeah, nah, idk))
}
```

```{r Q8}
q8_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    to_likert("Q8_study")
) %>%
  set_names(subfields)

q8_q4 <- map(
  types, ~ analysis %>%
    filter(Q4_quantqual == .x) %>%
    to_likert("Q8_study")
) %>%
  set_names(types)

gen$q8 <- append(q8_q3, q8_q4)
gen$q8$Everyone <- to_likert(col_prefix = "Q8_study")
```

```{r Q10}
q10_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    to_likert("Q10_phen")
) %>%
  set_names(subfields)

q10_q4 <- map(
  types, ~ analysis %>%
    filter(Q4_quantqual == .x) %>%
    to_likert("Q10_phen")
) %>%
  set_names(types)

gen$q10 <- append(q10_q3, q10_q4)
gen$q10$Everyone <- to_likert(col_prefix = "Q10_phen")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")

gen %>%
  saveRDS("data/generated.rds")
```
